### 2021-12-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@9c57188839a677c080e4176c35e8c6b2dc8c20eb 🚀
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@9193efcaedf173b7998a227d8497953cfac19103 🚀

@@

>>>>

Intro

@@

\textbf{Acknowledgements:} We acknowledge that this study was conducted
on land within the traditional unceded territory of the Saint Lawrence
Iroquoian, Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak
nations. This research was enabled in part by support provided by Calcul
Québec (www.calculquebec.ca) and Compute Canada (www.computecanada.ca).
